---
author: '**David Kleinhans**'
date: 'Frankfurt am Main, 2019'
institution: 'Johann Wolfgang Goethe-Universität'
division: 'Entwicklungsbiologie der Vertebraten'
advisor: 'Prof. Dr. Sven Klimpel'
altadvisor: 'Prof.Dr. Virginie Lecaudey'
department: 'Fachbereich Biowissenschaften'
degree: '**PhD in Biology**'
title: '**Morphogenesis in the _D.rerio_ Posterior Lateral Line Primordium**'
knit: "bookdown::render_book"
site: bookdown::bookdown_site
output: 
  thesisdown::thesis_pdf: default
#  thesisdown::thesis_gitbook: default
#  thesisdown::thesis_word: default
#  thesisdown::thesis_epub: default
# If you are creating a PDF you'll need to write your preliminary content here or
# use code similar to line 20 for the files.  If you are producing in a different
# format than PDF, you can delete or ignore lines 20-31 in this YAML header.
#abstract: |
#  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = '\n  ')`
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab is 
# needed on the line after the |.,

acknowledgements: |
  I thank my colleagues
  Since most of my analysis is based on 10 fish of Stocknumber 161-1, I also thank those.
  
dedication: |
  I dedicate this Thesis to...
  
  1. my sister,
  
  2. my grandma, 
  
  3. my mom,
  
  4. my dad, 
    
  5. my friends,
  
preface: |
  "You realize when you know _how_ to think, it empowers you far beyond those who know only _what_ to think" - Neil Degrasse Tyson
bibliography: files/library.bib
csl: files/science.csl
lot: true
lof: true
disclosure: |
  Disclosure: Unless otherwise noted, all figures in this manuscript are an expression of my own creative achievement. Similarities between molecule, protein and signalling models exist and are based on well-known textbooks such as Lodish et al., Molecular Cell Biology, 5th Edt. and Scott F. Gilbert et al., Developmental Biology 11th Edt. 
#space_between_paragraphs: true
#- \usepackage{tikz}
---

```{r include_packages, include = FALSE}
if(!require(devtools))
  install.packages("devtools", repos = "http://cran.rstudio.com")
if(!require(thesisdown))
  devtools::install_github("ismayc/thesisdown")
library(thesisdown)
```

```{r chunkopts, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, fig.align='center', 
                      dev.args=list(bg="transparent"), dev='png') #, dev='pdf'
library(pROC)
#library(plyr)
#library(dplyr)
#library(data.table)
library(ggplot2)
library(ggpubr)
library(pander)
library(kableExtra)
library(magrittr)
#library(ggpaired)
```
<!-- You'll need to include the order that you'd like Rmd files to appear in the _bookdown.yml file for
PDF files and also delete the # before rmd_files: there.  You'll want to not include 00(two-hyphens)prelim.Rmd
and 00-abstract.Rmd since they are handled in the YAML above differently for the PDF version.
-->

# Zusammenfassung {.unnumbered}

# Summary {.unnumbered}

# List of Abbreviations {.unnumbered}

| **Index** 	| **Abbrev.** 	| **Elaboration**                                 	|
|-----------	|-------------	|-------------------------------------------------	|
|           	| 2-/3-D       	| Two or Three Dimensional                         	|
|           	| A.I.        	| apical index                                    	|
|           	| CC          	| Cell Cluster                                    	|
|           	| CNN         	| Convolutional Neural Network                    	|
|           	| dpf         	| days post fertilization                         	|
|           	| DSH         	| Dishevelled                                     	|
|           	| ECDF        	| Empirical Cumulative Distribution Function      	|
|           	| Fgf         	| Fibroblast Growth Factor                        	|
|           	| Fgfr1       	| Fgf receptor 1                                  	|
|           	| FOV         	| Field of View                                   	|
|           	| FRZ         	| Frizzled                                        	|
|           	| IJ          	| ImageJ                                          	|
|           	| ISH         	| In Situ Hybridization                           	|
|           	| KDE         	| Kernel Density Estimation                       	|
|           	| l.e.        	| leading edge                                    	|
|           	| LL          	| Lateral Line                                    	|
|           	| LOESS       	| locally weighted scatterplot smoothing          	|
|           	| LOESS       	| Locally Weighted Scatterplot Smoothing          	|
|           	| LSFM        	| Light sheet fluorescence microscope             	|
|           	| LUT         	| Lookup Table                                    	|
|           	| MaxIP       	| Maximum Intensity Projection                    	|
|           	| MO          	| Morpholino                                      	|
|           	| N.A.        	| Numerical Aperture                              	|
|           	| NICD        	| Notch intracellular domain                      	|
|           	| NM          	| Neuromast                                       	|
|           	| NMII        	| Non muscle myosin II                            	|
|           	| p.Hist      	| phospho-Histone                                 	|
|           	| PCR         	| Polymerase chain reaction                       	|
|           	| PFA         	| Paraformaldehyd                                 	|
|           	| PLLp        	| Posterior Lateral Line Primordium               	|
|           	| Rock        	| Rho-Kinase                                      	|
|           	| ROI         	| Region of Interest                              	|
|           	| SBD         	| Shroom binding domain                           	|
|           	| SEM         	| Scanning Electron Microscopy                    	|
|           	| SNR         	| Signal to Noise Ratio                           	|
|           	| TALEN       	| Transcription activator-like effector nuclease  	|
|           	| TF          	| Transcription Factor                            	|
|           	| wt          	| Wild Type                                       	|
