---
author: '**David Kleinhans**'
date: 'May 2018'

institution: 'Goethe University Frankfurt am Main'
division: 'Developmental Biology of Vertebrates'
advisor: 'Prof.Dr. Virginie Lecaudey'
altadvisor: 'Prof.Dr. Manfred Schliwa'
department: 'Institute for Cell Biology and Neuroscience'
degree: '**PhD in Biology**'
title: '**Morphogenesis in the _D.rerio_ Posterior Lateral Line Primordium**'
knit: "bookdown::render_book"
site: bookdown::bookdown_site
output: 
  thesisdown::thesis_pdf: default
#  thesisdown::thesis_gitbook: default
#  thesisdown::thesis_word: default
#  thesisdown::thesis_epub: default
# If you are creating a PDF you'll need to write your preliminary content here or
# use code similar to line 20 for the files.  If you are producing in a different
# format than PDF, you can delete or ignore lines 20-31 in this YAML header.
#abstract: |
#  `r if(knitr:::is_latex_output()) paste(readLines("00-abstract.Rmd"), collapse = '\n  ')`
# If you'd rather include the preliminary content in files instead of inline
# like below, use a command like that for the abstract above.  Note that a tab is 
# needed on the line after the |.,

acknowledgements: |
  I thank my colleagues
  Since most of my analysis is based on 10 fish of Stocknumber 161-1, I also thank those.
  
dedication: |
  I dedicate this Thesis to...
  
  1. my sister,
  
  2. my grandma, 
  
  3. my mom,
  
  4. my dad, 
    
  5. my friends,
  
preface: |
  "You realize when you know _how_ to think, it empowers you far beyond those who know only _what_ to think" - Neil Degrasse Tyson
bibliography: bib/library.bib
# Download your specific bibliography database file and refer to it in the line above.
csl: csl/nature.csl
# Download your specific csl file and refer to it in the line above.
lot: true
lof: true
#space_between_paragraphs: true
#- \usepackage{tikz}
---

```{r include_packages, include = FALSE}
# This chunk ensures that the thesisdown package is
# installed and loaded. This thesisdown package includes
# the template files for the thesis.
if(!require(devtools))
  install.packages("devtools", repos = "http://cran.rstudio.com")
if(!require(thesisdown))
  devtools::install_github("ismayc/thesisdown")
library(thesisdown)
```

```{r chunkopts, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, cache=FALSE, autodep=TRUE, cache.comments=FALSE, warning=FALSE, out.width='75%\\textwidth', fig.align='center', include=TRUE, message=FALSE, dev.args=list(bg="transparent"), dev='pdf') #, dev='pdf' #, cache=TRUE #, cache.comments=FALSE
library(pROC)
library(plyr)
library(dplyr)
library(data.table)
library(ggplot2)
library(ggpubr)
library(pander)
#library(ggpaired)
```
<!-- You'll need to include the order that you'd like Rmd files to appear in the _bookdown.yml file for
PDF files and also delete the # before rmd_files: there.  You'll want to not include 00(two-hyphens)prelim.Rmd
and 00-abstract.Rmd since they are handled in the YAML above differently for the PDF version.
-->

# Zusammenfassung {.unnumbered}

# Summary {.unnumbered}

# List of Abbreviations {.unnumbered}

--------------------------------------------------------------------------------------------
 **index**   **Abbrev.**  **Elaboration**
----------- ------------- ------------------------------------------------------------------- 
 **0-9**      2-D	            Two Dimensional

              3-D 	          Three Dimensional

 **C**        CC  	          Cell Cluster

 **E**        ECDF 	          Empirical Cumulative Distribution Function

 **K**        KDE  	          Kernel Density Estimation

 **L**        LL 	            Lateral Line

              LOESS  	        Locally Weighted Scatterplot Smoothing

              LUT	            Lookup Table

 **M**        MaxIP  	        Maximum Intensity Projection

 **N**        NM  	          Neuromast

 **P**        PFA  	          Paraformaldehyd

              PLLp  	        Posterior Lateral Line Primordium

 **R**        ROI  	          Region of Interest

 **S**        SEM 	          Scanning Electron Microscopy

 **W**        WT	            Wild Type
--------------------------------------------------------------------------------------------
